A star formation event in the leading arm of the Magellanic stream triggered by passage through the outer Galactic disk

### 2018-11-02 ms.tex
Ack

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Ekta Patel (Arizona),
Josh Peek (STScI),
Anil Seth (\todo{where?}),
and Erik Tollerud (STScI)
for useful suggestions and discussion.

@@

\todo{Dylan Simon, Nick Carreiro and SCC at Flatiron}

\todo{Flatiron Institute}

>>>>

It is a pleasure to thank
Lauren Anderson (Flatiron),
Ana Bonaca (Harvard),
Elena D'Onghia (UW Madison),
Dan Foreman-Mackey (Flatiron),
Raja Guhathakurta (UCSC),
Cliff Johnson (Northwestern),
Ekta Patel (Arizona),
Josh Peek (STScI),
Anil Seth (Utah),
and Erik Tollerud (STScI)
for useful suggestions and discussion.

@@

We thank the Scientific Computing Core at the Flatiron Institute, and especially Dylan Simon and Nick Carriero, for technical support and access to the Flatiron Institute cluster computing resources, which enabled this work.
We thank the Center for Computational Astrophysics and especially David Spergel for support, access to computational resources, and space to conduct this work.
